The Shape and Color of Politics

### 2023-09-22 chapter_2/src/slides/slides.qmd
successfully published on github pages with the gh-pages branch

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs: 
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
  cache: true
---

>>>>

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
---
